Stay in shape! Homework exam II

### 2016-03-31 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
expended 1a even more

		$C$ bounding linesegments cross the x-axis 2 times and
			the disk border is intersected at least 2 times by non x axis
			parralel bounding linesegments.

>>>>

		$C$ bounding linesegments cross the x-axis 2 times and
			the disk border is intersected at least 2 times by non x axis
			parralel bounding linesegments, one linesegment intersects the
			left part of the disk and another the right part.
			An alternative defintion is not case 1,2 and 4.
